\mytitle

### 2012-05-23 papers/SAS2012/implicitization.tex
separation entre version format LMCS et version format article ou amsart

\documentclass{llncs}

\usepackage{ifxetex}
\ifxetex
\else
\usepackage[utf8]{inputenc}
\fi

\usepackage{amsmath}
\usepackage{mathcomp,amsfonts,amssymb}
\usepackage[mathscr]{euscript}
\usepackage{algorithmic,algorithm}
\usepackage{paralist}
\usepackage{graphicx}
%\usepackage{color}
\usepackage{placeins}

\usepackage{enumitem}
\usepackage{dcolumn}
\usepackage{rotating}

\usepackage{listings}
\lstset{language=C,mathescape=true,numbers=left,numbersep=0.8ex,tabsize=2,breaklines=true,basicstyle={\rm\fontfamily{phv}\small\selectfont}}

\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}

\tikzstyle{state}=[circle,fill=black!25,minimum size=13pt,inner sep=0pt]
\tikzstyle{rstate}=[rectangle,fill=black!25,minimum size=13pt,inner sep=0pt]
\tikzstyle{transition}=[rectangle,semithick,draw=black!75,
  			  minimum size=4mm]
\tikzstyle{transition2}=[transition,rectangle,thick,dashed,
  			  minimum size=4mm]
\tikzstyle{PRstate}=[circle,double,draw,fill=blue!15,minimum size=13pt,inner sep=0pt]
\tikzstyle{polyhedra}=[blue!25,opacity=0.5,pattern=north west lines,pattern
color=blue]
\tikzstyle{line}=[black,thick]

\newcommand{\mytitle}{Succinct Representations for Abstract Interpretation}
\usepackage[pdftitle={\mytitle},pdfauthor={Julien Henry, David Monniaux, Matthieu Moy}]{hyperref}

\newcommand{\abstr}[1]{#1^\sharp}
\newcommand{\parts}[1]{\mathscr{P}(#1)}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\widening}{\mathop{\triangledown}}

\graphicspath{{figures/}{gnuplot/}}

% commentaires dans les algorithmes crees avec le package algorithmic
\renewcommand{\algorithmiccomment}[1]{ {\color{gray} // #1}}

\usepackage{ifthen}
\newboolean{draft}
%\setboolean{draft}{true}
\setboolean{draft}{false}

\ifthenelse{\boolean{draft}}{
  \newcommand{\avirer}[1]{{\color{red} #1}}
  \newcommand{\MM}[1]{{\color{blue} TODO(MM): #1}}
  \newcommand{\JH}[1]{{\color{teal} TODO(JH): #1}}
  \newcommand{\DM}[1]{{\color{violet} TODO(DM): #1}}
}{
  \newcommand{\avirer}[1]{}
  \newcommand{\MM}[1]{}
  \newcommand{\JH}[1]{}
  \newcommand{\DM}[1]{}
}

\title{\mytitle}
\subtitle{Combined analysis algorithms and experimental evaluation}
\author{Julien Henry\inst{1}\inst{2} \and David Monniaux\inst{1}\inst{3} \and Matthieu Moy\inst{1}\inst{4}}

\institute{VERIMAG laboratory, Grenoble, France
\and Université Joseph Fourier
\and CNRS
\and Grenoble-INP}

\renewcommand{\baselinestretch}{1}

\begin{document}
\maketitle

@@

\FloatBarrier

\phantomsection\addcontentsline{toc}{section}{References} 
\bibliographystyle{splncs03}
\bibliography{implicitization}

\appendix

\MM{TODO: la partie appendix est laissée en chantier. A priori, on ne
  mettra que les tableaux de chiffres sans les commentaires, et les
  tableaux risquent de changer avec les avancées de Julien.}

\section{Experimental Results}

Experimental results of our tool on the benchmark presented in
Fig~\ref{fig:projects} are given below. The precision of different
techniques is given in Table~\ref{tab:techniques}. The precision of
abstract domains and widening operators in given in
Table~\ref{tab:domain}.

\begin{sidewaystable}
\begin{center}
\setlength{\tabcolsep}{0.75ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{G/S}}
& \multicolumn{3}{c|}{\textbf{PF/S}}
& \multicolumn{3}{c|}{\textbf{PF/G}}
& \multicolumn{3}{c|}{\textbf{G+PF/PF}}
& \multicolumn{3}{c|}{\textbf{G+PF/G}}
& \multicolumn{3}{c|}{\textbf{DIS/G+PF}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table1}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focusing} (PF), our combined technique (G+PF), and its version using
disjunctive invariants (DIS). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm.
$\subsetneq$, $\supsetneq$ and ``unc.'' are defined as in Fig.~\ref{fig:techniques}.}
\label{tab:techniques}
\end{sidewaystable}

\label{sec:compare_domains}
\begin{sidewaystable}
\begin{center}
\setlength{\tabcolsep}{0.75ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{PK/OCT}}
& \multicolumn{3}{c|}{\textbf{PK/BOX}}
& \multicolumn{3}{c|}{\textbf{OCT/BOX}}
& \multicolumn{3}{c|}{\textbf{PK/PKEQ}}
& \multicolumn{3}{c|}{\textbf{PK/GRID}}
& \multicolumn{3}{c|}{\textbf{POLY/POLY*}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table_domain.tex}
\end{tabular}
\end{center}
\caption{Results of the comparison of the various abstract domains, when using
the same technique (G+PF). We used as abstract domains Convex Polyhedra (PK and
POLY),
Octagons (OCT), intervals (BOX), linear equalities (PKEQ) and linear congruences
(GRID). The last column compares the domain of Convex Polyhedra with the
improved widening operator from \cite{BagnaraHRZ05SCP} (POLY*), and Convex Polyhedra
using the classical widening operator (POLY). POLY and POLY* use the Parma
Polyhedral Library \cite{PPL}.
$\subsetneq$, $\supsetneq$ and ``unc.'' are defined as in Fig.~\ref{fig:techniques}.}
\label{tab:domain}
\end{sidewaystable}

\end{document}

>>>>

\maketitle

@@
